\section{General description}

In this course you will learn about one of the most important skills of the data scientist: data visualisation.  We will focus on using visualisation to understand problems and clearly explain your research to others.  We will also be applying statistics and machine learning algorithms that you will learn in other parts of the course to conduct a number of small analysis projects.

\subsection{Relationship with other teaching units}

This course will rely heavily on material learned in the statistics module.

\section*{Form of course}

One of the most important aspects of working with data is being able to communicate your results clearly with your colleagues and clients.  As such, an integral part of this course will be explaining the results of each week's work to your classmates, and asking and answering each other questions.

Each week we will start with presentations of the previous week's work.  After that new material and R code examples will be given, before we start work on the current week's work.

Some weeks the problems will require coding and then presenting your plots and results, and other weeks problems will be conceptual or mathematical in nature. Some weeks I will ask you to work in small groups and sometimes individually.

\section*{Workload}

There will be assignments given each week.  There will be time to work on them and get help during class.  In addition I have scheduled 5 hours per week to work on them outside class.  Please complete all the work.
