\section{Course Program}


Lecture notes for each week will be uploaded after class.  All of the problem sets will be handed out during class.


\subsection*{Week One}

Introduction to data visualisation with R.  We will go over the anatomy of a good plot, and learn how to make some standard types of plot in R.  Exercises will require you to make a certain types of plots from a data set that will be provided.

\subsection*{Week Two}

Making the right plot to answer the question.  We will learn how to answer questions by making a plot.  This week will involve lots of examples, some group work and then some individual coding tasks.  The exact plot you need to make will no longer be given - you need to work it out.

\subsection*{Week Three}

Functional forms, how to characterise different behaviour, correlations.  Often when you plot two variables you can see some correlation between them.  We will learn how to describe different types of functional relationship and suggest mathematical formulae that may be appropriate for fitting.

\subsection*{Week Four}

Fitting data, interpolation and predictions.  We will apply techniques from the machine learning lectures to a specific problem.  We will discuss the importance of understanding the underlying data to guide the extent of our predictions.

\subsection*{Week Five}

Showing distributions, averages, errors, combining errors.  We will talk about performing measurements including their errors.

\subsection*{Week Six}

Hypotheses and designing experiments.  Now we will think about how to ask a good question, and then design an experiment to answer it.  There will be some group work where you are asked to design experiments to test certain hypotheses.

\subsection*{Week Seven}

Working on the final project.  Everyone will complete their own project.

\subsection*{Week Eight}

Present final projects and revision.  You will be presenting the results from your final project to your classmates.  Everyone will be presenting their work and answering questions.



