\documentclass{beamer}
\newif\ifplacelogo
\placelogotrue
\mode<presentation>{\usetheme{Boadilla2}}

\usepackage{geometry}
\usepackage{color}
\usepackage{graphicx}

\usepackage[T1]{fontenc}
\usepackage{fontspec}
\setmainfont{CenturyGothic}
\setsansfont{CenturyGothic}

\AtBeginSection[]{\frame{\tableofcontents[currentsection]}}

\definecolor{myturquoise}{RGB}{0,176,176}
\definecolor{mylightturquoise}{RGB}{54,216,216}


\begin{document}


\setlength{\unitlength}{1mm}
\title{DS Visualisation and Analysis}
\author[Abbey Waldron]{Abbey Waldron}
\date[October 16th, 2015]{}




\setbeamertemplate{navigation symbols}{}

{
\placelogofalse
\begin{frame}
  \titlepage
\end{frame}
}



\begin{frame}{Experiment Presentations and Final Projects}

\begin{enumerate}
\item Presentations of your experiments!
\item Introduction to your Final Projects
\item Everyone start work on final projects
\end{enumerate}

\end{frame}


\begin{frame}{Experiments}

\end{frame}

\begin{frame}{What should be in your presentation?}

\begin{enumerate}
\item A description of the problem you have been given (everyone has different tasks so they won't know!)
\item Examples of real life situations/companies where this may occur
\item Description of your experiment, with a detailed timeline and plan
\item Discussion of difficulties you expect, ethical considerations etc.~any of the above questions that yielded interesting anwsers
\end{enumerate}


\end{frame}


\begin{frame}{Presentations}

\begin{enumerate}
\item Bread
\item Students
\item Sneakers
\item Cows
\item Travel website
\item Bar
\end{enumerate}

\end{frame}


\begin{frame}{Final Projects - Timeline}

he deadline to hand the work in is October 30th, 2015 at 11:20 am, on paper to\
 me.

\vspace{5mm}

You should include a written report including your answers to all of the questions.  These should consist of plots, explanations and/or numbers where appropriate.  In addition, you must attach your code to the back of the document.

\end{frame}

\begin{frame}{Final Projects - Timeline}


You will all have to give a short (5 min) presentation of your work in class starting at 08:30 on October 30th.  It is fine to just show your plots or reports, I will be asking questions!
\end{frame}


\begin{frame}{Final Projects}

\end{frame}


\begin{frame}{Next Week}

We meet again on the 30th October.  

\begin{itemize}
\item You will all present your results (required)
\item You will hand in your reports
\item We will do some preparation for the exam
\end{itemize}

\end{frame}

\begin{frame}{Good Luck!}

\end{frame}






%%%%%%%%%%%%% backup slides %%%%%%%%%%%%%%%%%%%%%%%%

\appendix
\newcounter{finalframe}
\setcounter{finalframe}{\value{framenumber}}

\begin{frame}{Backup Slides}
\end{frame}




\setcounter{framenumber}{\value{finalframe}}

\end{document}
